\policy{Respect in (and out of) the Classroom}{
I expect everyone to treat, and be treated, with respect in our classroom. Every one of us brings something new, interesting, and engaging to the topics that we will discuss. This does not mean you cannot disagree and express disagreements; however, we can all expect that each other does so with the respect we desire to be treated with ourselves.\\

The central commitment of American University is the development of thoughtful, responsible human beings in the context of a challenging yet supportive academic community. The \href{https://www.american.edu/policies/students/student-conduct-code.cfm}{Student Code of Conduct} is designed to benefit the American University community and to assist in forming the highest standards of ethics and morals among its members. By registering for this course, students have acknowledged their awareness of the Student Code of Conduct and they are obliged to become familiar with their rights and responsibilities as defined by the Code.\\

\href{https://www.american.edu/policies/au-community/upload/disrimination-and-sexual-harassment-policy-09-05-19-final.pdf}{American University expressly prohibits any form of discrimination and discriminatory harassment} including sexual harassment, dating and domestic violence, sexual assault, and stalking. As a faculty member, \emph{I am required to report} discriminatory or harassing conduct to the university if I witness it or become aware of it--regardless of the location of the incident. The same is true if I believe that you are in danger of harm or in danger of harming someone else. There are four confidential resources on campus if you wish to speak to someone who is not required to report: \href{https://www.american.edu/ocl/counseling/}{Counseling Center}, \href{https://www.american.edu/ocl/promote-health/oasis.cfm}{victim advocates in OASIS}, medical providers in the \href{https://www.american.edu/ocl/healthcenter/}{Student Health Center}, and ordained clergy in the \href{https://www.american.edu/ocl/kay/}{Kay Spiritual Life Center}. If you experience any of the above, you have the option of filing a report (details about how can be found on the \href{https://www.american.edu/equity-titleix/help.cfm}{Office of Equity \& Title IX}). For more information, including a list of supportive resources see the Office's \href{https://www.american.edu/equity-titleix/support.cfm}{support guide}.
}

\policy{Academic Integrity}{
You are expected to follow university guidelines regarding academic integrity on all assignments (graded or not). I expect that you will provide appropriate credit through citation and acknowledgement of others' ideas while you take this class. I am required to report all suspected violations of the university's code of conduct to the Dean and will do so when I suspect plagiarism or academic dishonesty.\\

Standards of academic conduct are set forth in the university’s Academic Integrity Code. By registering for this course, you have acknowledged your awareness of the \href{https://www.american.edu/academics/integrity/code.cfm}{Academic Integrity Code} and you must become familiar with your rights and responsibilities as defined by the Code. 
}

\policy{Religious Observances}{
Students will be provided the opportunity to make up any examination, study, or work requirements that may be missed due to a religious observance, provided they notify their instructors before the end of the second week of classes. Please send this notification through email to the professor. For additional information, see American University’s \href{http://www.american.edu/ocl/kay/Major-Religious-Holy-Days.cfm}{religious observances policy}.
}
