\subsection{Academic Support and Access Center (ASAC) MGC 243,
202-885-3360.} All students may take advantage of the Academic
Support and Access Center (ASAC) for individual academic skills,
counseling, workshops, tutoring and writing assistance, as well
as Supplemental Instruction. All services are free. The services
include the Writing Center (first floor of Bender Library), which
assists students with academic writing and assignments. The
Math/Stat Lab (Myers Building, 202-885-3154) which provides
mathematics and statistics tutoring. Additional content tutoring
is also available in the ASAC's Tutoring Lab.

\subsection{Students with Disabilities, ASAC} American University
is committed to making learning and programming as accessible as
possible. Students who wish to request accommodations for a
disability, must notify me with a letter of approved
accommodations from the ASAC. As the process for registering and
requesting accommodations can take some time, and as
accommodations, if approved, are not retroactive, I strongly
encourage students to contact the ASAC as early as possible. For
more information about the process for registering and requesting
disability-related accommodations, contact ASAC.

\subsection{Counseling Center MGC 214, 202-885-3500.} The
Counseling Center helps students make the most of their
university experience, both personally and academically. We offer
individual and group counseling, urgent care, self-help
resources, referrals to private care, as well as programming to
help you gain the skills and insight needed to overcome adversity
and thrive while you are in college. Contact the Counseling
Center to make an appointment in person or by telephone, or visit
the Counseling Center page on the AU website for additional
information.

\subsection{Center for Diversity \& Inclusion MGC 201,
202-885-3651.} CDI is dedicated to enhancing LGBTQ,
Multicultural, First Generation, and Women's experiences on
campus and to advance AU's commitment to respecting \& valuing
diversity by serving as a resource and liaison to students,
staff, and faculty on issues of equity through education,
outreach, and advocacy.

\subsection{OASIS: The Office of Advocacy Services for
Interpersonal and Sexual Violence McCabe Hall 123, 202-885-7070,
oasis@american.edu.} OASIS provides free and confidential
advocacy services for students who experience sexual assault,
dating or domestic violence, sexual harassment, and/or stalking.
Please email or call to schedule an appointment with one of the
two victim advocates in OASIS.

\begin{itemize} \tightlist \item American University expressly
prohibits any form of discriminatory harassment including sexual
harassment, dating and domestic violence, sexual assault, and
stalking. The university is and equal opportunity, affirmative
action institution that operated in compliance with applicable
laws and regulations, and does not discriminate on the basis of
race, color, national origin, religion, sex (including
pregnancy), age, sexual orientation, disability, marital status,
personal appearance, gender identity and expression, family
responsibilities, political affiliation, source of income,
veteran status, an individual's genetic information or any other
bases under federal or local laws in its programs and activities.
\item If you experience any of the above, you have the option of
filing a report with the AU Department of Public Safety
202-885-2527 or the Office of the Dean of Students 202-885-3300
\href{mailto:dos@american.edu}{dos@american.edu}. To file a Title
IX complaint, contact the Title IX Program Officer 202-885-3373
or \href{mailto:TitleIX@american.edu}{TitleIX@american.edu}.
Please keep in mind that all faculty and staff -- with exception
of counselors in the Counseling Center, victim advocates in
OASIS, medical providers in the Student Health Center, and
ordained clergy in the Kay Spiritual Life Center -- who are aware
of or witness this conduct are required to report this
information to the university, regardless of the location of the
incident. \end{itemize}

\subsection{International Student \& Scholar Services, Batelle
4th Butler Pavilion, Room 410.} ISS has resources to support
academic success and participation in campus life including
academic counseling, support for second language learners,
response to questions about visas, immigration status and
employment and intercultural programs, clubs and other campus
resources.
